Bootstrap Confidence Intervals for Regression Discontinuity Designs

### 2016-02-14 main_paper.tex
Moving forward on Section 2

\title{Bootstrap confidence intervals for regression discontinuity estimators
  with the uniform kernel}
\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He}

@@

\section{Background}\label{background}

>>>>

\title{Bootstrap Confidence Intervals for Regression Discontinuity Designs}
\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors: 
Department of Economics, Iowa State University. 260 Heady Hall, Ames, IA  50011.
Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
He: yanghe@iastate.edu.}}

@@

\section{Background}\label{background}
In the typical sharp RD setting, a researcher wishes to estimate the local 
causal effect of treatment at a given threshold. The running variable, $X_{i}$, 
determines treatment assignment.  Given a known threshold, $\bar{x}$, set to 
zero without loss of generality, a unit receives treatment if $X_{i} \geq 0$ or 
does not receive treatment if $X_{i} < 0$. Let $Y_{i}(1)$ and $Y_{i}(0)$ denote 
the potential outcomes for unit $i$ given it receives treatment and
 in the absence of treatment, respectively. Hence, the observed sample is 
 comprised of the running variable, $X_{i}$, and
 \begin{align}
  Y_{i}=Y_{i}(0) \mathbbm{1}\{X_{i}<0\}+Y_{i}(1) \mathbbm{1}\{X_{i} \geq 0\}
 \end{align}
where $\mathbbm{1}\{ \cdot\}$ denotes the indicator function. For convenience, 
define
 \begin{align}
  \mu(x)= \mathbbm{E}[Y_{i}|X_{i}=x]
 \end{align}
Also, let $\mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}$ be the $\eta^{th}$ 
derivative of the unknown regression function and define 
$\mu^{(\eta)}_{+}=lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x)$ and 
$\mu^{(\eta)}_{-}=lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x)$.
In most cases the population parameter of interest is 
$\tau=\mathbbm{E}[Y(1)-Y(0)|X=\bar{x}]$ (i.e., the average treatment effect 
at the threshold). Under continuity and smoothness conditions on both the 
conditional distribution of $X_i$ and the first moments of $Y(0)$ and $Y(1)$ at
the cutoff, $\tau$ is nonparametrically identifiable (Hahn, Todd and Van der 
Klaauw, 2001) by:
\begin{align}
 \tau&= \mu_{+}- \mu_{-} \nonumber \\ 
&\text{ where } \mu_{+}=lim_{x \rightarrow 0^{+}}\mu(x),\text{ and } 
\mu_{-}=lim_{x \rightarrow 0^{-}}\mu(x)
\end{align}

Naturally, the estimation of $\tau$ in RD designs focuses on the 
problem of approximating $\mathbbm{E}[Y(1)|X=x]$ and $\mathbbm{E}[Y(0)|X=x]$ 
near the cutoff. Due to its desirable properties when estimating regression 
functions at boundary points, we consider the popular approach of fitting 
separate kernel-weighted local linear regressions in neighborhoods on both 
sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
\cite{FanGijbels92} for discussions of the properties of local polynomial 
regressions for boundary problems.The results presented here are valid for
higher order polynomials and discontinuities at derivatives, like ``Kink RDD''
in Card, Lee and Pei (2009). We focus on the linear case for ease in exposition.}
For the local linear model, we use the following estimator as described in 
Calonico, Cattaneo and Titiunik (2014)\footnote{Throughout the paper we follow the
notation on Calonico, Cattaneo and Titiunik (2014) very closely.}
\begin{align*}
 \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= argmin_{b_{0},b_{1}} 
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
\end{align*}
where $K_{h}(x_{i}) = K\left(\frac{x_{i}}{h}\right)\frac{1}{h}$.
